### 2023-06-29 introduction.tex
section intro
up

% trop d'hypotheses trop fortes sur les WSTS
\alain{harmonier les noms des pb}
\noindent
{\bf Our contributions}
\begin{itemize}
%\item We investigate and expand upon the notion of state-resilience ~\cite{DBLP:journals/corr/PrasadZ16,DBLP:journals/corr/PrasadZ16,DBLP:journals/corr/abs-2108-00889,DBLP:conf/gg/Ozkan22} and we study three decidability questions for each of type of resilience. We remark that it is an instance of the home-space problem~\cite{DBLP:journals/corr/abs-2207-02697,memmi2023invariants}.

@@

Safety requires that only one aircraft at a time attempts to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy, i.e. 
 the contents of a counter can spontaneously get lower at any time.
 Lossiness is represented by using transitions decreasing any counter by one from every state. 
% We ask however that the system is not too lossy. We add the condition that for every prefix of an execution, the number of ``lossiness transition'' for a counter is less than nine tenth of the number of transitions incrementing said counter.
In this example, the safe, desirable state would be one where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while explicit resilience or $k$-resilience asks whether they will do so in at most $k$ steps. 
Explicit resilience is of interest since in general we want to ensure the safe space will \alain{on n'utilise nulle part le terme explicit resilience....}
be reached in
the least amount of steps possible. 
In this exemple, for instance, aircrafts cannot simply wait in the air an infinite amount of time. Fortunately, $8$-resilience hold in the example.
\end{example}

>>>>

% trop d'hypotheses trop fortes sur les WSTS
\noindent
{\bf Our contributions}
\begin{itemize}
%\item We investigate and expand upon the notion of state-resilience ~\cite{DBLP:journals/corr/PrasadZ16,DBLP:journals/corr/PrasadZ16,DBLP:journals/corr/abs-2108-00889,DBLP:conf/gg/Ozkan22} and we study three decidability questions for each of type of resilience. We remark that it is an instance of the home-space problem~\cite{DBLP:journals/corr/abs-2207-02697,memmi2023invariants}.

@@

Safety requires that only one aircraft at a time attempts to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy, i.e. 
 the contents of a counter can spontaneously get lower at any time.
 Lossiness is represented by using transitions decreasing any counter by one from every state. 
% We ask however that the system is not too lossy. We add the condition that for every prefix of an execution, the number of ``lossiness transition'' for a counter is less than nine tenth of the number of transitions incrementing said counter.
In this example, the safe, desirable state would be one where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while $k$-resilience asks whether they will do so in at most $k$ steps. 
$k$-resilience is of interest since in general we want to ensure the safe space will 
be reached in
the least amount of steps possible. 
In this exemple, for instance, aircrafts cannot simply wait in the air an infinite amount of time. Fortunately, $8$-resilience hold in the example.
\end{example}

### 2023-06-29 resilience.tex
up

\alain{pourquoi redire ça, c'est dans l'intro : In this section we introduce the concepts of resilience, bounded-resilience and $k$-resilience for well structured transition systems. We show that the resilience problems are decidable
for  completion-post-effective $\omega^2$-WSTS with strong compatibility
with $\Safe=\uparrow \Safe$,
and that resilience is decidable for downward-compatible ideal-effective WSTS
when $\Safe=\downarrow \Safe$. 
We show that the three resilience problems are however undecidable for WSTS with
strong compatibility in general.}

>>>>

% \alain{pourquoi redire ça, c'est dans l'intro : In this section we introduce the concepts of resilience, bounded-resilience and $k$-resilience for well structured transition systems. We show that the resilience problems are decidable for  completion-post-effective $\omega^2$-WSTS with strong compatibility with $\Safe=\uparrow \Safe$, and that resilience is decidable for downward-compatible ideal-effective WSTS when $\Safe=\downarrow \Safe$.  We show that the three resilience problems are however undecidable for WSTS with strong compatibility in general.}
